---
title: "Get started with quiver"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get started with quiver}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| label: knitr-setup
#| include: false
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
#| label: setup
library(quiver)
```

A quiver holds arrows so they're within reach the moment you need one.
This package does the same job for [Agent Skills](https://www.anthropic.com/news/skills): a `SKILL.md` with instructions, plus whatever reference files it needs, kept somewhere an agent can reach it.
quiver copies that folder into place, and remembers what it copied — so later, it can tell you whether you've hand-edited it since.

## A source to install from

quiver draws skills from a _source_.
This vignette uses `local_source()`, which treats a directory as a checkout of a skills repository: skills live under `skills/<name>/`, each with its own `SKILL.md`.
A skill can also be installed straight from 'GitHub' with `github_source()` — see [Installing straight from 'GitHub'](#installing-straight-from-github) below.

This vignette builds a local source from scratch so the example is fully runnable.
In practice, `path` would be a checkout of a real skills repository sitting on disk.

```{r}
#| label: build-source
checkout <- withr::local_tempdir()

skill_dir <- file.path(checkout, "skills", "demo-skill")
dir.create(skill_dir, recursive = TRUE)
writeLines(
  c(
    "---",
    "name: demo-skill",
    "description: A minimal example skill.",
    "---",
    "",
    "# Demo skill",
    "",
    "Say hello."
  ),
  file.path(skill_dir, "SKILL.md")
)

source <- local_source(checkout)
```

## Installing a skill

`quiver_install()` takes a skill from the source and puts it where the given `agent` reads skills from.
`quiver_agents()` lists the agents quiver knows how to install for:

```{r}
#| label: agents
quiver_agents()
```

Skills install at project scope (under a project directory) or user scope (in the agent's directory under the user's home).
This vignette uses an isolated temporary directory as the project, so nothing here touches your actual machine:

```{r}
#| label: install
project <- withr::local_tempdir()

quiver_install("demo-skill", source, agent = "claude", path = project)
```

The skill now lives under `.claude/skills/demo-skill/` inside `project`, alongside the other files Claude reads.

## Checking status

`quiver_status()` reports what's installed, and whether any installed skill has been hand-edited since quiver installed it — its on-disk checksum no longer matches what was written:

```{r}
#| label: status
quiver_status(agent = "claude", path = project)
```

Editing a file inside the installed skill and checking again shows the change:

```{r}
#| label: status-after-edit
writeLines(
  "Say hello, warmly.",
  file.path(project, ".claude", "skills", "demo-skill", "SKILL.md")
)

quiver_status(agent = "claude", path = project)
```

By default, `quiver_install()` leaves a hand-edited skill alone rather than clobbering it — installing again with the same name is a no-op unless you pass `force = TRUE`.

## Removing a skill

`quiver_remove()` pulls an installed skill back out.
A hand-edited skill stays put unless `force = TRUE`, the same protection `quiver_install()` gives it:

```{r}
#| label: remove
quiver_remove("demo-skill", agent = "claude", path = project, force = TRUE)

quiver_status(agent = "claude", path = project)
```

## Installing straight from 'GitHub'

Skills don't need a local checkout first: `github_source()` installs
straight from a 'GitHub' repository, finding any `SKILL.md` in the tree —
whether the repo uses a flat `skills/<name>/` layout or groups skills
under categories.

Three catalogue constructors wrap `github_source()` for known skill
catalogues, so you don't need to remember the repository slug: `?ropensci_skills`,
`?posit_skills`, and `?rladies_grimoire`. These need a network connection,
so they're not run in this vignette:

```r
quiver_install("package-review", ropensci_skills(), agent = "claude")
quiver_install("testing-r-packages", posit_skills(), agent = "claude")
quiver_install("rladies-blog-post", rladies_grimoire(), agent = "claude")
```

## What's next

A curated registry source is next, so a skill can be installed from a
catalogue without knowing its repository at all — see the
[README](https://github.com/drmowinckels/quiver#status) for current status.
