---
title: "Get started with quiver"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get started with quiver}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(quiver)
```

An [Agent Skill](https://www.anthropic.com/news/skills) is a folder: a
`SKILL.md` with instructions, plus whatever reference files it needs. quiver
copies that folder to wherever an agent expects to find it, and remembers
what it copied, so it can tell you later whether you've hand-edited it.

## A source to install from

quiver installs skills from a *source*. The only source it knows about today
is `local_source()`, which treats a directory as a checkout of a skills
repository: skills live under `skills/<name>/`, each with its own
`SKILL.md`.

This vignette builds one from scratch so the example is fully runnable. In
practice, `path` would be a checkout of a real skills repository sitting on
disk.

```{r build-source}
checkout <- withr::local_tempdir()

skill_dir <- file.path(checkout, "skills", "demo-skill")
dir.create(skill_dir, recursive = TRUE)
writeLines(
  c(
    "---",
    "name: demo-skill",
    "description: A minimal example skill.",
    "---",
    "",
    "# Demo skill",
    "",
    "Say hello."
  ),
  file.path(skill_dir, "SKILL.md")
)

source <- local_source(checkout)
```

## Installing a skill

`quiver_install()` copies a skill from the source into the directory the
given `agent` reads skills from. `quiver_agents()` lists the agents quiver
knows how to install for:

```{r agents}
quiver_agents()
```

Skills can be installed at project scope (under a project directory) or user
scope (in the agent's directory under the user's home). This vignette uses
an isolated temporary directory as the project, so it doesn't touch
anything on your actual machine:

```{r install}
project <- withr::local_tempdir()

quiver_install("demo-skill", source, agent = "claude", path = project)
```

The skill now lives under `.claude/skills/demo-skill/` inside `project`,
alongside the other files Claude reads.

## Checking status

`quiver_status()` reports what's installed, and whether any installed skill
has been hand-edited since quiver installed it — its on-disk checksum no
longer matches what was written:

```{r status}
quiver_status(agent = "claude", path = project)
```

Editing a file inside the installed skill and checking again shows the
change:

```{r status-after-edit}
writeLines(
  "Say hello, warmly.",
  file.path(project, ".claude", "skills", "demo-skill", "SKILL.md")
)

quiver_status(agent = "claude", path = project)
```

By default, `quiver_install()` leaves a hand-edited skill alone rather than
clobbering it — installing again with the same name is a no-op unless you
pass `force = TRUE`.

## Removing a skill

`quiver_remove()` deletes an installed skill. A hand-edited skill is left in
place unless `force = TRUE`, the same protection `quiver_install()` gives
it:

```{r remove}
quiver_remove("demo-skill", agent = "claude", path = project, force = TRUE)

quiver_status(agent = "claude", path = project)
```

## What's next

This release only ships `local_source()`. A 'GitHub' source and a curated
registry source are planned, so skills can be installed straight from a
repository or a catalogue without a local checkout first — see the
[README](https://github.com/drmowinckels/quiver#status) for current status.
